---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 4.5,
  fig.align = "center",
  fig.path = "figs/"
)
```
# Project Title

<!-- badges: start -->
<!-- badges: end -->

One Paragraph of the project description.

- [Getting Started](#getting-Started)
  - [Prerequisites](#prerequisites)
  - [Installing](#installing)
- [Usage](#usage)
- [Authors](#authors)
- [Contributing](#contributing)
- [Acknowledgments](#acknowledgments)

## Getting Started

### Prerequisites

Requirements for the software and other tools to build, test and push 
- [Example 1](https://www.example.com)
- [Example 2](https://www.example.com)

### Installing

A step by step series of examples that tell you how to get a development
environment running

Say what the step will be

    Give the example

```{r cars}
summary(cars)
```


## How To Use

> [!NOTE]
> This is a note.

```{r pressure, echo = FALSE}
plot(pressure)
```

## Authors

  - **[Someone](https://github.com/PurpleBooth)** 

> [Something](https://github.com/) &nbsp;&middot;&nbsp;
> GitHub [@javiermtz](https://github.com/) &nbsp;&middot;&nbsp;

See also the list of
[contributors](https://github.com/)
who participated in this project.

## Contributing

Pull requests are welcome. For major changes, please open an issue first
to discuss what you would like to change.

Please make sure to update tests as appropriate.

## Acknowledgments

  - This template is based on Billie Thompson's template - [README Template](https://github.com/PurpleBooth/a-good-readme-template#readme)

## References

---

